Consistency scores in text data

### 2020-07-08 outputs/documents/paper.Rmd
Write-up fixes, still WIP

@@

In recent years, pre-trained language models have tremendous contributions in advancing a wide range of diverse natural language processing (NLP) tasks such as reading comprehension, text generation, and many others. The pre-trained models enables (citation). As the pre-trainde models remove the need for researchers and technologists to train models from scratch, they promote faster growth and advancement int he field of NLP. OpenAI GPT-3 is the latest generative pre-trained language model released by OpenAI in 2020. It has 175 billion parameters and is trained to [do that and that]. GPT-2, the predecessor of GPT-3, employs a semi-supervised approach that combines unsupervised pre-training and supervised fine-tuning where task-specific data set and task-specific fine-tuning were still needed in achieving these tasks until the birth of GPT-3 (citation). GPT-3 removes such needs, and its task-agnostic nature enables the accessible creation of cutting-edge NLP applications.

GPT-3 learns like human do — with brief directive and simple instruction...

@@

>>>>

/// Start of  OpenAI GPT-3 section ///

In recent years, pre-trained language models have tremendous contributions in advancing natural language processing (NLP) tasks such as reading comprehension, text generation, and many others (citation). As the pre-trained models remove the need for researchers and technologists to train models from scratch, they promote faster growth and advancement int the field of NLP. OpenAI GPT-3 is the latest generative pre-trained language model released by OpenAI in 2020. It has 175 billion parameters and is trained to [do that and that]. GPT-2, the predecessor of GPT-3, employs a semi-supervised approach that combines unsupervised pre-training and supervised fine-tuning where task-specific data set and task-specific fine-tuning were still needed in achieving these tasks until the birth of GPT-3 (citation). GPT-3 removes such needs, and its task-agnostic nature enables the accessible creation of cutting-edge NLP applications.

GPT-3 learns like humans do — with brief directives and simple instruction...

/// End of  OpenAI GPT-3 section ///

@@

@@

Without exception, all human languages have some words that co-occur more frequently with others. Under this assumption, we can regard the production of English text as a set of conditional probabilities, written as Pr($w_{k}$ | $w^{k-1}_{1}$), where $w_{k}$ is the predicted word, and $w^{k-1}_{1}$ is the history of the word occurring in a sequence (citation). In other word, the generation of prediction $w_{k}$ is based on the history $w^{k-1}_{1}$. [Add a sentence linking to n-gram]

N-gram is a sequence of n words. Taking the imcomplete first sentence from the Jane Eyre excerpt as an example:

> "There was no possibility of..."

"There" is a unigram, "There was" is a bigram, "There was no" is a trigram, and "There was no possibility of" is a 5-gram. On the other hand, the trigrams of the excerpt are "There was no," "was no possibility," and "no possibility of." The overlapping chaining of words reveals the statistical behaviour in human language. Moreover, N-gram then enables us to assign a probability to the occurrence of a sequence of words or the likelihood of a word occurring next.

[Maybe include N to do more statistics write up]

The application of n-gram is versatile. N-gram is widely applied in text prediction and spelling-correction...
